Stateless Model Checking with Data-Race Preemption Points

### 2016-03-23 oopsla-16/intro.tex
Write about experimental setup.
Wow factor of verif

We present \quicksand,
a model checking framework for deciding at runtime which preemption points to test,
according to which resulting state spaces are most likely to fit a prescribed CPU budget.
It uses data-race analysis \cite{eraser} to dynamically find new preemption points which expose bugs not reachable by preempting on API calls alone.
When prior work would time out on large tests by trying several preemption points simultaneously,
\quicksand~tests smaller state spaces based on subsets of those points, which often finds the same bugs sooner.
On the other hand, when the CPU budget is large enough to fully test all data-race preemption points,
we prove that this constitutes a total verification of all possible thread schedules.
Short of deciding in advance to preempt on every single instruction \cite{spin}, this was not previously possible without data-race preemption points.

>>>>

% TODO: Incorporate the following point
% On the other hand, techniques such as ICB assume all state spaces will be too big, and optimize the search to uncover bugs more quickly, but at the expense of / by sacrificing the ability to complete a total verification quickly when possible.

We present \quicksand,
a model checking framework for deciding at runtime which preemption points to test,
according to which resulting state spaces are most likely to fit a prescribed CPU budget.
It uses data-race analysis \cite{eraser} to dynamically find new preemption points which expose bugs not reachable by preempting on API calls alone.
When prior work would time out on large tests by trying several preemption points simultaneously,
\quicksand~\revision{identifies these pitfalls in advance using state space estimation \cite{estimation},
and instead}~tests smaller state spaces based on subsets of those points.
\revision{Often, testing these}~smaller state spaces can even find the same bugs sooner.

On the other hand, when the CPU budget is large enough to fully test all data-race preemption points,
we prove that this constitutes a total verification of all possible thread schedules.
%Short of deciding in advance to preempt on every single instruction \cite{spin}, this was not previously possible without data-race preemption points.
\revision{To achieve the same level of verification, prior model checkers must decide}~in advance to preempt on every single memory access \cite{spin}, \revision{which is computationally prohibitive for
%even moderately-sized
larger tests.
Our approach provides the best of both worlds:
by estimating the size of the test on-the-fly, \quicksand~can find bugs quickly in large tests {\em and} provide fast total verification for small ones.}
